Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
spacing

The outer function call @nd@ evaluates over the set of possible closures of
@f@. For each such closure, we go into its body with a new environment and a new store.
Remember that the function @aeval@ returns a set of @VS@ objects to its continuation,
so the continuation argument @bodyvss@ is a set of @VS@ objects which represent values
from multiple computation paths when evaluating this single @body@ expression.

We next consider the inner call of function @nd@ which evaluates over the set of body values @bodyvss@.
For each @VS@, the timestamp and store in @VS@ will be instantiated to
@aeval@.
The inner application of @aeval@ returns a set of values of one computation path to its
continuation, where the continuation will accumulate the result and transfer
evaluation to the next body value.

@@

If the expression is atomic, then we just need to construct a new instance of
@VS@, return it to the @continue@ function.

>>>>

The outer call to @nd@ evaluates over the set of possible closures of
@f@. For each such closure, we go into its body with a new environment and a new store.
Remember that the function @aeval@ returns a set of @VS@ objects to its continuation,
so the continuation argument @bodyvss@ is a set of @VS@ objects which represent values
from multiple computation paths when evaluating this single @body@ expression.

We next consider the inner call to @nd@, which evaluates over the set of body values @bodyvss@.
For each @VS@, the timestamp and store in @VS@ will be instantiated to
@aeval@.
The inner application of @aeval@ returns a set of values of one computation path to its
continuation, where the continuation will accumulate the result and transfer
evaluation to the next body value.

@@

If the expression is atomic, then we simply need to construct a new instance of
@VS@ and return it to the @continue@ function.
